%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{Software Engineer} % Job title
{Adobe} % Organization
{San Francisco Bay Area} % Location
{Nov. 2020 - Present} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Developed scalable Kotlin and Java services powering Adobe Aero, the Content Platform, and the Commerce Platform, with a focus on high availability, cost efficiency, and fault tolerance across multi-cloud environments.}
\item {Led the design and implementation of a queue-based BlobStore garbage collection service, reducing storage costs and improving system reliability across cloud regions.}
\item {Drove the delivery of the ``Copy Blob by ID'' feature with AWS and Azure cross-region support, enabling faster blob replication and improving overall system throughput.}
\item {Optimized cloud spend by auditing and decommissioning unused infrastructure and services across teams, resulting in measurable operational cost savings.}
\item {Built an LLM-powered feature flag cleanup bot that automatically removes stale flags from codebases using a Renovate-style dashboard, reducing technical debt and simplifying configuration management.}
\item {Led the migration from Splunk to Prometheus and Alertmanager for metrics and alerting; evangelized adoption across engineering orgs by hosting knowledge sharing sessions, and creating onboarding documentation.}
\item {Reduced PR test suite execution times by over 50\% and improved CI reliability through targeted test optimization, resulting in faster iteration loops and higher developer productivity.}
\item {Influenced external partner teams to improve resiliency and reduce error rates by identifying integration weaknesses and proposing robust solutions, significantly reducing order loss during high-traffic events.}
\item {Partnered with external teams to decouple payment logic from the ordering pipeline, simplifying future integrations with payment methods and improving the maintainability of the ordering system.}
\item {Led critical contributions to high-impact initiatives including B2C Stack Unification, B2B Switch Plan, and B2B Self-Cancel, resolving cross-team dependencies and delivering features that contributed to millions in revenue.}
\item {Led the migration of multiple high-throughput services from Cassandra to DynamoDB, improving scalability, operational simplicity, and overall service reliability.}
\item {Developed an automated cross-system cache invalidation mechanism triggered by tax or country configuration changes, eliminating manual processes and ensuring data consistency across services.}
\item {Mentored and onboarded engineers by creating comprehensive documentation, leading design walkthroughs, and sharing domain-specific best practices across teams.}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Software Engineer Intern} % Job title
{IBM} % Organization
{Markham, Ontario, Canada} % Location
{May 2018 - April 2020 (24 months)} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Designed and developed a NodeJS CLI tool that scans a project's open source dependencies and generates a report for review by the legal team. Reduced an entirely manual effort to a single automated Jenkins cron job.}
\item {Developed an automated E2E regression testing suite capable of running multiple types of tests such as Selenium WebDriver, AVA, and JUnit on TravisCI. Reduced the number of regressions by 50\%.}
\item {Implemented gRPC and Go microservices within a crucial data pipeline for Guardium Insights.}
\item {Leveraged ReactJS, AngularJS, and NodeJS to develop responsive components and features for the Guardium Insights frontend.}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}
